---
title: "   "
author: "SDIV"
---

## Homework 001 due date: september 16, 2024-12:00:00

1.  Read [Sec 1.1, pp 1-2 @Sutton2018] and answer the following.

Explain why Reinforcement Learning differs for supervised and unsupervised
learning.

2.  See the first Steve Brunton's youtube video about [Reinforcement
    Learning.](https://www.youtube.com/watch?v=0MNVhXEX9to&list=PLMrJAkhIeNNQe1JXNvaFvURxGY4gE9k74)
    Then accordingly to its presentation explain what is the meaning of the
    following expression: $$
      V_{\pi}(s) = \mathbb{E}
     \left(
       \sum_{t} \gamma ^ {t} r_t | s_0 = s
     \right).
    $$

3.  Form [Sec. 1.7 @Sutton2018] obtain a time line pear year from 1950 to 2012.
    Use the following format [see
    https://kim.quarto.pub/milestones--bar-timelines/](https://kim.quarto.pub/milestones--bar-timelines/)

```{r}
library(bibtex)
## Activate the Core Packages
biblio <- bibtex::read.bib("../references.bib")
library(tidyverse) ## Brings in a core of useful functions
library(gt)        ## Tables
## Specific packages
library(milestones)
## Initialize defaults
## Initialize defaults
column <- lolli_styles()

data <- read_csv(col_names=TRUE, show_col_types=FALSE, file='rl_time_line.csv')

## Sort the table by date
data <- data |>
  arrange(date)

## Build a table
gt(data) |>
  #cols_hide(columns = event) |>
  tab_style(cell_text(v_align = "top"),
            locations = cells_body(columns = date)) |>
  tab_source_note(source_note = "Source: Sutton and Barto (2018)") 
```

```{r}
## Adjust some defaults
column$color <- "orange"
column$size  <- 15
column$source_info <- "Source: Sutton and Barto (2018)"

## Milestones timeline
milestones(datatable = data, styles = column)
```
